% Auto-generated cluster examples (verbatim evidence + paraphrase).

\subsubsection*{Cluster 1: Parking space requirements by use}
\noindent\textbf{Instrument description:} This cluster collects minimum parking-space requirements tied to land-use categories. Parking rules are typically calculated by capacity (seats, beds, employees) or floor area, and apply to uses such as churches, hotels, hospitals, community facilities, boarding houses, home occupations, and other commercial/industrial uses. One clause also addresses yard/open space demarcation to avoid double counting.

\noindent\textbf{Keywords (TF-IDF):} space, ft, parking space, plot, sq, sq ft, parking, plus, building, area, floor, floor area

\begin{itemize}[leftmargin=*]
\item
\textbf{Requirement:} Parking space required: one space per four seats or bench seating capacity.

\begin{quote}\footnotesize Auditoriums, assembly halls, dance halls, theaters, gymnasiums, and skating rinks: One space for each four seats or bench seating capacity.\end{quote}
\noindent\texttt{doc=akron-register-tribune\_\_1974-09-26 | chunk=akron-register-tribune\_\_1974-09-26::sec003 | motive=infrastructure\_coordination | modality=must}
\item
\textbf{Requirement:} One parking space per sleeping room for boarding/rooming houses.

\begin{quote}\footnotesize Boarding, rooming or lodging house: One space for each sleeping room.\end{quote}
\noindent\texttt{doc=akron-register-tribune\_\_1974-09-26 | chunk=akron-register-tribune\_\_1974-09-26::sec003 | motive=infrastructure\_coordination | modality=must}
\end{itemize}

\subsubsection*{Cluster 5: Off-street loading and parking standards}
\noindent\textbf{Instrument description:} Regulates off-street loading/unloading spaces, including access from streets or alleys and all-weather surface requirements. Also sets parking-related dimensions and location rules, such as driveway width (12–25 feet) and stalls within 300 feet on premises (employees up to 1,000 feet). It additionally requires dwelling-unit abutment of 25 feet along a public street.

\noindent\textbf{Keywords (TF-IDF):} feet, street, loading, 25, 25 feet, spaces, driveways, employee, 300, alley, access, street alley

\begin{itemize}[leftmargin=*]
\item
\textbf{Requirement:} Loading/unloading space with access from a street or alley and 14 feet vertical clearance must be provided.

\begin{quote}\footnotesize loading and unloading space with proper access from a street or alley, and with at least fourteen (14) feet of vertical clearance shall be provided, either within or outside the building to adequately serve the use on the lot.\end{quote}
\noindent\texttt{doc=akron-register-tribune\_\_1974-09-26 | chunk=akron-register-tribune\_\_1974-09-26::sec003 | motive=infrastructure\_coordination | modality=must}
\item
\textbf{Requirement:} All off-street loading spaces must have an all-weather surface.

\begin{quote}\footnotesize All off-street loading or unloading spaces shall have an all-weather surface to provide safe and convenient access and use during all seasons.\end{quote}
\noindent\texttt{doc=akron-register-tribune\_\_1974-09-26 | chunk=akron-register-tribune\_\_1974-09-26::sec003 | motive=infrastructure\_coordination | modality=must}
\end{itemize}

\subsubsection*{Cluster 8: Residential Home Occupation Restrictions}
\noindent\textbf{Instrument description:} Regulates home-based businesses in residential areas by restricting sales to items produced by the home occupation, prohibiting commercial-vehicle deliveries, and limiting activity to within the dwelling or permanent accessory structure. The occupation must be incidental to residential use, with limited staffing, no exterior alterations or changes to residential appearance, and no adverse impact on neighbors’ health, safety, or neighborhood character.

\noindent\textbf{Keywords (TF-IDF):} home, home occupation, occupation, premises, shall, residential, commercial, occupations, home occupations, produced, produced home, vehicle

\begin{itemize}[leftmargin=*]
\item
\textbf{Requirement:} No on-premises selling of articles or services unless they are produced by the home occupation.

\begin{quote}\footnotesize D) No article or service shall be sold or offered for sale on the premises, except such as is produced by such occupation.\end{quote}
\noindent\texttt{doc=ad-visor-and-chronicle\_\_2010-05-08 | chunk=ad-visor-and-chronicle\_\_2010-05-08::sec002 | motive=public\_health\_safety | modality=must\_not}
\item
\textbf{Requirement:} Home occupations must not use commercial vehicles for delivery to or from the premises; a commercial vehicle is defined by signage or other advertisement of the home occupation.

\begin{quote}\footnotesize H) A home occupation shall not involve the use of commercial vehicles for delivery of materials to or from the premises. For the purposes of this section, a commercial vehicle shall be defined as one with any sign, markings, address, telephone number, or other form of display that advertises or is associated with a home occupation on that premises.\end{quote}
\noindent\texttt{doc=ad-visor-and-chronicle\_\_2010-05-08 | chunk=ad-visor-and-chronicle\_\_2010-05-08::sec002 | motive=public\_health\_safety | modality=must\_not}
\end{itemize}

\subsubsection*{Cluster 9: Dumpster disposal restrictions}
\noindent\textbf{Instrument description:} This cluster enforces dumpster-based waste disposal rules, specifying acceptable materials and service access. It includes first-come, first-served operation, prohibitions on liquids, hazardous waste, Freon appliances, yard waste, and household garbage, plus conditions on dumpster availability and delivery restrictions.

\noindent\textbf{Keywords (TF-IDF):} disposal, shall acceptable, acceptable disposal, acceptable, shall, waste, waste shall, materials, prohibited, allowed, dumpster, service

\begin{itemize}[leftmargin=*]
\item
\textbf{Requirement:} The disposal event operates on a first-come, first-served basis.

\begin{quote}\footnotesize This is on first come, first service.\end{quote}
\noindent\texttt{doc=ad-visor-and-chronicle\_\_2010-05-08 | chunk=ad-visor-and-chronicle\_\_2010-05-08::sec003 | motive=infrastructure\_coordination | modality=must}
\item
\textbf{Requirement:} Liquid waste (paint, oil, chemicals, etc.) shall not be acceptable for disposal.

\begin{quote}\footnotesize Liquid Waste (paint, oil, Chemicals, Etc.)\end{quote}
\noindent\texttt{doc=ad-visor-and-chronicle\_\_2010-05-08 | chunk=ad-visor-and-chronicle\_\_2010-05-08::sec003 | motive=environmental\_protection | modality=must\_not}
\end{itemize}

\subsubsection*{Cluster 7: Non-conforming use regulations}
\noindent\textbf{Instrument description:} This cluster governs non-conforming uses, including how they may be extended within buildings and changed within the same structure, with limits on extending beyond the building and the effect of demolition on status. It also covers amortization or conformance timelines for non-conforming signs and allowances for ordinary repairs that do not increase the building's cubic content.

\noindent\textbf{Keywords (TF-IDF):} non, non conforming, conforming, conforming use, use, amendment, building, provided, conform, land, signs, structure

\begin{itemize}[leftmargin=*]
\item
\textbf{Requirement:} Non-conforming use may be extended within the parts of the building designed for such use (as of the time of adoption or amendment).

\begin{quote}\footnotesize Any non-conforming use may be extended throughout any of the parts of a building which were manifestly arranged or designed for such use at the time of adoption or amendment of this Ordinance,\end{quote}
\noindent\texttt{doc=akron-register-tribune\_\_1974-09-26 | chunk=akron-register-tribune\_\_1974-09-26::sec003 | motive=infrastructure\_coordination | modality=may}
\item
\textbf{Requirement:} Non-conforming use may not extend beyond the building.

\begin{quote}\footnotesize but no such use shall be extended to occupy any land outside such building.\end{quote}
\noindent\texttt{doc=akron-register-tribune\_\_1974-09-26 | chunk=akron-register-tribune\_\_1974-09-26::sec003 | motive=infrastructure\_coordination | modality=must\_not}
\end{itemize}
